Analysis

### 2023-02-28 Analysis.rmd
second test commit to test overleaf sync
Add standardised scores to performance table

colors <- RColorBrewer::brewer.pal(n = 9, name = "Set1")
```

@@

@@

```{r, performance-table}
make_performance_table <- function(scores) {
  scores |>
    filter(scale %in% c("log", "natural")) |>
    summarise_scores(by = c("model", "target_type", "scale", "horizon")) |>
    filter(horizon == 2) |>
    select(model, target_type, scale, interval_score, coverage_50, coverage_90) |>
    pivot_wider(names_from = scale, values_from = interval_score) |>
    select(model, target_type, natural, log, coverage_50, coverage_90) |>
    mutate(across(c(where(is.numeric)), signif, digits = 2)) |>
    arrange(target_type, model) |>
    kable(format = "latex", booktabs = TRUE, 
          align = c("l", "l", rep("c", 4)),
          caption = "Performance for two-week-ahead forecasts \\label{tab:scores}",
          linesep = c('', '', '', '\\addlinespace'),
          col.names = c("Model", "Target", "WIS", "WIS (log scale)", 
                        "Coverage 50%", "Coverage 90%")) |> 
    kable_styling(latex_options = c("scale_down", 
                                    "hold_position")) 
}

scores |>
  filter(model %in% models_non_human) |>
  make_performance_table() |>
  cat(file = 'manuscript/performance-table.tex')

>>>>

colors <- RColorBrewer::brewer.pal(n = 9, name = "Set1")

@@

```{r}
scores_standardised <- scores |>
  filter(scale %in% c("log", "natural")) |>
  filter(model %in% models_non_human) |>
  summarise_scores(by = c("model", "target_type", "scale", "horizon", "forecast_date")) |>
  filter(horizon == 2) |>
  group_by(target_type, scale) |>
  mutate(interval_score = (interval_score - mean(interval_score)) / sd(interval_score)) |>
  group_by(model, target_type, scale) |>
  summarise(mean = mean(interval_score)) |>
  pivot_wider(names_from = scale, values_from = mean, names_prefix = "stand_") |>
  arrange(target_type, model)
```

@@

```{r, performance-table}
make_performance_table <- function(scores, standardised_scores) {
  scores |>
    filter(scale %in% c("log", "natural")) |>
    summarise_scores(by = c("model", "target_type", "scale", "horizon")) |>
    filter(horizon == 2) |>
    select(model, target_type, scale, interval_score, coverage_50, coverage_90) |>
    pivot_wider(names_from = scale, values_from = interval_score) |>
    select(model, target_type, natural, log, coverage_50, coverage_90) |>
    inner_join(standardised_scores) |>
    mutate(across(c(where(is.numeric)), signif, digits = 2)) |>
    arrange(target_type, model) |>
    mutate(natural = paste0(natural, " (", stand_natural, ")"), 
           log = paste0(log, " (", stand_log, ")")) |>
    select(-stand_log, -stand_natural) |>
    kable(format = "latex", booktabs = TRUE, 
          align = c("l", "l", rep("c", 4)),
          caption = "Performance for two-week-ahead forecasts \\label{tab:scores}",
          linesep = c('', '', '', '\\addlinespace'),
          col.names = c("Model", "Target", "WIS", "WIS (log scale)", 
                        "Coverage 50%", "Coverage 90%")) |> 
    kable_styling(latex_options = c("scale_down", 
                                    "hold_position")) 
}

scores |>
  filter(model %in% models_non_human) |>
  make_performance_table(standardised_scores = scores_standardised) %>%
  gsub("\\{table\\}", "\\{table\\*\\}", x = .) |>
  cat(file = 'manuscript/performance-table.tex')
